\textsc{Does Copyright Affect Reuse?\\ Evidence from Wikipedia and the Google Books Digitization Project}

### 2016-09-13 writing/paper.tex
minor changes

\author{Abhishek Nagaraj \footnote{Haas School of Business, University of California, Berkeley. F565, 2220 Piedmont Ave, Berkeley, CA 94720-1900. I am thankful to Erik Brynjolfsson, Daniel Fehder, Jeff Furman, Avi Goldfarb, Shane Greenstein, Joshua Krieger, Matt Marx, Aruna Ranganathan, Fabian Waldinger, Pai-Ling Yin, participants of the Economic Sociology Working Group and MIT Economics Third Year Lunch and especially Pierre Azoulay, Scott Stern, Catherine Tucker and Heidi Williams for comments. All errors remain mine.}
\\         \texttt{nagaraj@berkeley.edu}   
}

>>>>

\author{Abhishek Nagaraj \footnote{Haas School of Business, University of California, Berkeley. F565, 2220 Piedmont Ave, Berkeley, CA 94720-1900. I am thankful to Erik Brynjolfsson, Daniel Fehder, Jeff Furman, Avi Goldfarb, Shane Greenstein, Joshua Krieger, Matt Marx, Aruna Ranganathan, Fabian Waldinger, Pai-Ling Yin, three anonymous referees, participants of the Economic Sociology Working Group and MIT Economics Third Year Lunch and especially Pierre Azoulay, Scott Stern, Catherine Tucker and Heidi Williams for comments. All errors remain mine.}
\\         \texttt{nagaraj@berkeley.edu}   
}
